---
title: "makeCodebook.Rmd"
author: "Jeff Renza"
date: "July 26, 2014"
output: html_document
---

Variable list and descriptions
------------------------------

Variable name    | Description
-----------------|------------
subject          | ID the subject who performed the activity for each window sample. Its range is from 1 to 30.
activity         | Activity name
featDomain       | Feature: Time domain signal or frequency domain signal (Time or Freq)
featInstrument   | Feature: Measuring instrument (Accelerometer or Gyroscope)
featAcceleration | Feature: Acceleration signal (Body or Gravity)
featVariable     | Feature: Variable (Mean or SD)
featJerk         | Feature: Jerk signal
featMagnitude    | Feature: Magnitude of the signals calculated using the Euclidean norm
featAxis         | Feature: 3-axial signals in the X, Y and Z directions (X, Y, or Z)
featCount        | Feature: Count of data points used to compute `average`
featAverage      | Feature: Average of each variable for each activity and each subject

Dataset structure
-----------------

```{r}
str(dt_tidy)
```

Key variables in the data table
-------------------------------

```{r}
key(dt_tidy)
```

Show a few rows of dataset
--------------------------

```{r}
dt_tidy
```

Summary of vars
---------------

```{r}
summary(dt_tidy)
```

List all possible combinations of features
------------------------------------------

```{r}
dt_tidy[, .N, by=c(names(dt_tidy)[grep('^feat', names(dt_tidy))])]
```

Save to file
------------

Save data table to a tab-delim. text file called 'HumanActivityRecognitionUsingSmartPhones_Dataset.txt'

```{r save}
file <- file.path('./', 'HumanActivityRecognitionUsingSmartPhones_Dataset.txt')
write.table(dt_tidy, file, quote=F, sep='\t', row.names=F)